A linearization procedure for constrained multibody systems

### 2012-03-26 PetersonGedeHubbard2012.tex
Added references.bib.
Changed wording in conclusion re pt. of lineariz
Minor changes
section 3 -> now titled discussion
fixed eq1 boldness
removed last paragraph in section 3

We see in Table \ref{table:assumptions} the differential equations which
describe our system. The goal of this procedure is to create linear equations
of motion with the following structure:
\begin{align}
    \label{eq:structure}
    \tilde{M} \dot{\bm{x}} = \tilde{A} \bm{x}_i + \tilde{B} r
\end{align}
where $\bm{x}$ is the state vector of all the coordinates and speeds and
$\bm{x}_i$ is the state vector of only the independent coordinates and speeds.
From this equation we can perform numerical integration or stability analysis,
or it can be reformulated into the traditional state space equations for
controller design.

@@

\section{Implementation and Examples}

@@

If it is found that substatial computational time is spent in computing the
jacobian matrices, it might be possible to reduce the time if the point of
linearization is known. We are taking the partial derivatives with respect to
$q$, $\dot{q}$, $u$, and $\dot{u}$ in a number of vectors. If we know the point
of linearization (have numerical values for $q$, $\dot{q}$, $u$, $\dot{u}$), we
can substitute all of the quantities except for those we are taking the
derivative with respect to; e.g. when computing $\nabla_{\bm{u}} \bm{f}_3$ we
substitute in the known values for $q$, $\dot{q}$, and $r$. In this situation,
the cost of symbolic substitution needs to be considered. In practice,
substituion is sometimes computationally expensive. A speed-up, which is not
not guaranteed, needs to be weighed against the loss of flexibility to choose a
point of linearization at a later time.

@@

\begin{enumerate}
    \item Describe the system in the form of the equations shown in Table
        \ref{table:assumptions}.
    \item Compute the quantities shown in equation (\ref{eq:quant_to_compute}).
    \item Either through inspection or performing a SVD on
        $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$
        and $\nabla_{\bm{u}} \bm{f}_{v} P_{ud}$, create the partition matrices
        $P_u$ and $P_q$ which correctly identify the independent coordinates and
        speeds.
    \item Form the quantities in equations (\ref{eq:C_0}), (\ref{eq:C_1}), and
        (\ref{eq:C_2}); using these terms and those from equation
        (\ref{eq:quant_to_compute}), form equation
        (\ref{eq:state_space_constrained}).
    \item Choose a point of linearization and:
        \begin{enumerate}
            \item integrate the equations of motion.
            \item reformulate the equations into the traditional state space form.
            \item perform stability analysis.
            \item perform other analyses.
        \end{enumerate}
\end{enumerate}

@@

\bibliography{library}   % name your BibTeX data base
\bibliographystyle{spmpsci}      % mathematics and physical sciences
\end{document}

>>>>

We see in Table \ref{table:assumptions} the differential equations which
describe our system. The goal of this procedure is to create linear equations
of motion with the following structure:
\begin{align}
    \label{eq:structure}
    \tilde{M} \dot{\bm{x}} = \tilde{A} \bm{x}_i + \tilde{B} \bm{r}
\end{align}
where $\bm{x}$ is the state vector of all the coordinates and speeds and
$\bm{x}_i$ is the state vector of only the independent coordinates and speeds.
From this equation we can perform numerical integration or stability analysis,
or it can be reformulated into the traditional state space equations for
controller design.

@@

\section{Discussion}

@@

@@

\begin{enumerate}
    \item Describe the system in the form of the equations shown in Table
        \ref{table:assumptions}.
    \item Compute the quantities shown in equation (\ref{eq:quant_to_compute}).
    \item Either through inspection or performing a SVD on
        $\nabla_{\bm{q}}\bm{f}_{c} P_{qd}$
        and $\nabla_{\bm{u}} \bm{f}_{v} P_{ud}$, create the partition matrices
        $P_u$ and $P_q$ which correctly identify the independent coordinates and
        speeds.
    \item Form the quantities in equations (\ref{eq:C_0}), (\ref{eq:C_1}), and
        (\ref{eq:C_2}); using these terms and those from equation
        (\ref{eq:quant_to_compute}), form equation
        (\ref{eq:state_space_constrained}).
    \item Choose a point of linearization which satisfies the equations in
        Table \ref{table:assumptions} and:
        \begin{enumerate}
            \item integrate the equations of motion.
            \item reformulate the equations into the traditional state space form.
            \item perform stability analysis.
            \item perform other analyses.
        \end{enumerate}
\end{enumerate}

@@

\bibliography{references}   % name your BibTeX data base
\bibliographystyle{spmpsci}      % mathematics and physical sciences
\end{document}
